---
output: rmarkdown::github_document
---

```{r include=FALSE}
knitr::opts_chunk$set(
  fig.width=10, fig.retina=2, message=FALSE, warning=FALSE, collapse=TRUE
)
```

# psl

  Extract Internet Domain Components Using the Public Suffix List

## Description

The 'Public Suffix List' (<https://publicsuffix.org/>) is a collection of top-level domains ('TLDs') which include global top-level domainsa ('gTLDs') such as '.com' and '.net'; country top-level domains ('ccTLDs') such as '.de' and '.cn'; and, brand top-level domains such as '.apple' and '.google'. Tools are provided to extract internet domain components using the public suffix list base data.

- `libpsl`: <https://github.com/rockdaboot/libpsl>
- Public Suffix List: <https://publicsuffix.org/>
 
## What's Inside The Tin

The following functions are implemented:

- `apex_domain`:	Return the apex/top-private domain from a vector of domains
- `is_public_suffix`:	Test whether a domain is a public suffix
- `public_suffix`:	Return the public suffix from a vector of domains
- `suffix_extract`:	Separate a domain into component parts
- `suffix_extract2`:	Separate a domain into component parts (urltools compatible output)

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/psl")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(psl)
library(tidyverse)

# current verison
packageVersion("psl")

```

```{r message=FALSE, warning=FALSE, error=FALSE}
doms <- c(
  "", "com", "example.com", "www.example.com",
  ".com", ".example", ".example.com", ".example.example", "example",
  "example.example", "b.example.example", "a.b.example.example",
  "biz", "domain.biz", "b.domain.biz", "a.b.domain.biz", "com",
  "example.com", "b.example.com", "a.b.example.com", "uk.com",
  "example.uk.com", "b.example.uk.com", "a.b.example.uk.com", "test.ac",
  "cy", "c.cy", "b.c.cy", "a.b.c.cy", "jp", "test.jp", "www.test.jp",
  "ac.jp", "test.ac.jp", "www.test.ac.jp", "kyoto.jp", "test.kyoto.jp",
  "ide.kyoto.jp", "b.ide.kyoto.jp", "a.b.ide.kyoto.jp", "c.kobe.jp",
  "b.c.kobe.jp", "a.b.c.kobe.jp", "city.kobe.jp", "www.city.kobe.jp",
  "ck", "test.ck", "b.test.ck", "a.b.test.ck", "www.ck", "www.www.ck",
  "us", "test.us", "www.test.us", "ak.us", "test.ak.us", "www.test.ak.us",
  "k12.ak.us", "test.k12.ak.us", "www.test.k12.ak.us"
)

apex_domain(doms)

public_suffix(doms)

is_public_suffix(doms)

suffix_extract(doms)

suffix_extract2(doms) # urltools compatible output
```

```{r bench, message=FALSE, warning=FALSE, error=FALSE, fig.width=10, fig.retina=2}
library(microbenchmark)

microbenchmark(
  urltools = urltools::suffix_extract(doms),
  psl = psl::suffix_extract(doms), # returns more data
  psl2 = psl::suffix_extract2(doms) # returns what urltools does
) -> mb

autoplot(mb)
```